%!TEX root = Main_Assignment2.tex
\documentclass[Main_Assignment2]{subfiles}
\begin{document}

\begin{enumerate}[label=RE\arabic*:]
	\item 
	The device shall project current time onto the ceiling.
	
	\item 
	The device must be battery-driven.

	\item
	The device must use 1 AAA battery.

	\item
	The alarm shall make a BEEP sound.

	\item 
	The alarm shall make a visual stroboscope signal using the projector.

	\item
	The bottom of the device shall be partially rubberized, to prevent sliding.

	\item
	The device shall have 7 buttons: ON, PRJ, TI, ALM, SET, RPT, HH and MM.

	\item
	The device shall have one projection laser

	\item
	The device shall have one LED display

	\item
	The LED display shall display time in the following format:

	\begin{itemize}
		\item [I] [O-HH:MM] (shows alarm time – no repeat)
		\item [II] [R-HH:MM] (shows alarm time – repeat)
		\item [III] [T-HH:MM] (shows current time)

	\end{itemize}

	\item
	Pressing the ON button shall toggle the device between the ON and OFF state.

	\item
	Pressing the PRJ button shall toggle the projector between the ON and OFF state.	

	\item
	Pressing TI shall make the device show current time on the display.

	\item
	Pressing ALM shall make the device show alarm time on the display.

	\item
	Pressing SET, while the device is showing current time enables changing of the current time.

	\item
	Pressing SET, while the device is showing alarm time enables changing of the alarm time.

	\item
	Pressing SET while changing of current or alarm time is enabled disables changing of current or alarm time respectively.

	\item
	While changing current or alarm time is enabled, pressing HH will add one hour to the displayed time. If the number of hours exceed 23 the hours will reset to 00.

	\item
	While changing current or alarm time is enabled, pressing MM will add one minute to the displayed time. If the number of minutes exceed 59 the minutes will reset to 00.

	\item 
	Pressing RPT, while the device is showing alarm time toggles the alarm repeat function.

	\item
	When the alarm repeat function is enabled the alarm will reappear three times every five minutes and then stop.

	\item
	When the alarm repeat function is disabled the alarm only sounds once for 10 seconds.

	\item
	When the projector is ON, it always shows the current time.

\end{enumerate}
\end{document}