\documentclass[10pt, a4]{article}

\include{Preamble}
\title{Ceiling Projection Travel Alarm Clock} 
\author{Rasmus Bækgaard -- 10893, Rene Nilsson -- 10783, Kasper Nielsen -- 10731}

\begin{document}
\maketitle


\section{Plan and schedule the necessary activities} 

All activities must be broken down in smaller bit in a Plan-Driven.
This is due to a static hardware setup and no customer to interact with.
\\
\\
The following must be included as activities:
\begin{enumerate}
	\item Validate user requirements
	\item Hardware/software interface
	\item Software breakdown
	\begin{itemize}
		\item Display driver
		\item Projector driver
		\item Clock and alarm driver
		\item Sound driver
		\item Button driver
	\end{itemize}
	\item Software architecture and interfaces + test specification
	\item Development + unit tests
	\item Integration + integration tests
	\item Accept test
	\item Manual
\end{enumerate}



\section{What are the risks and how do you deal with them?}

\begin{enumerate}
	\item Kids -- should they get sick they need parental care.
	\item Sick days for all team members.
	\item Team members quiting the job.
	\item New tools makes people quit.
	\item Software scares the hardware designer away.
	\item Competing products are released before this product.
	\item Nobody wants to buy a clock -- people has smart phones\dots
\end{enumerate}
To deal with these risk, the company creates a probability and assessment analysis:

\begin{itemize}
	\item[1] Each member with kids are assigned to tasks which are given longer time to finish.
	\item[2] Flu season will hit along with common sickness ordinary people tends to catch.
	\item[3] Make documentation on the fly.
	\item[4] Make time for getting to know the new tools.
	\item[5a] The hardware designer must not be set to develop trivial software
	\item[5b] Offer the hardware designer classes in software development
	\item[6] Don't get delayed.
	\item[7] Marketing problem.
\end{itemize}

\section{Assign the staff to the activities. It is spring time and development will commence on 1 September.}



\section{How do you achieve the appropriate level of quality?}



\section{It is important that you are on time. 
Otherwise the company is expected to suffer substantial financial loss. 
	Which work could you sacrifice in order to meet the deadline in case unexpected delays occur?}






\end{document}